\Large \bf Frontrunning

### 2018-08-16 frontrunning/Latex/sections/paper.tex

\section{Introduction}
% Why is this important.
% PAPER BEING SOLD HERE

@@

\subsection{Front Running on the Blockchains}

@@

%What is Bancor and how it can be frontrun:%
\subsubsection{Bancor} %frontrunning by network participants.

Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.

@@

\subsubsection{Domain Name Registration}

%"domain name frontrunning." The practice resulted in Network Solutions registering a previously-unregistered domain to itself immediately after someone searched for it, then holding the domain for four days before it could be purchased by someone else or at another registrar. But the company claims that it's merely trying to protect customers from others doing exactly that. Until there is more regulation over frontrunning from ICANN, this is the best it can come up with

%Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
%
% PoC of frontrunning ghazal
Although frontrunning attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Frontrunning can occur within other blockchain based applications such as naming systems. Blockchain-based namespaces have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduces single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, frontrunning attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can frontrun other user's \textit{registerdomain} at a good profit by paying higher transaction fees. In both cases the adversarial party could sell the domain name to the users for higher price.
%TODO: also talk about ENS

@@

\subsection{Application design to prevent frontrunning}
Applications, in this case Dapps, could be designed in a way to prevent frontrunning.

\begin{itemize}
\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \dots} while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}. Commitment scheme is a good method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Another use of such commitment scheme, is in Decentral DNS, such as Ghazal or ENS. User will send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user sends a reveal transaction revealing the bid and also the details of the requested domain.

>>>>

\section{Introduction}
% Why is this important.
% PAPER BEING SOLD HERE
%______________________________________________________________%

@@

\subsection{Front Running on the Blockchains}
\label{sec:Front Running on the Blockchains}

@@

%What is Bancor and how it can be frontrun:%
\subsubsection{Bancor} \hfill\\
\noindent Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.

@@

\subsubsection{Domain Name Front-running} \hfill\\    %Following section talks about frontrunning in namespaces but limited to Ghazal. Will talk about NameCoin in the section of mitigations (commit & reveal method)
\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.
% PoC of frontrunning ghazal
%TODO: also talk about ENS

@@

\subsection{Application Design to Prevent Front-running}

Another way of preventing the front-running activities is to design the applications, whether they are decentralized (Dapps) or centralized, in such a way that no information would be available to the malicious parties which enables them to front-run the other users.
Followings discuss the two techniques which can be used by the Apps/DApps developers while designing the systems to prevent front-running activities.

\begin{itemize}
\item{\textbf{Commitment scheme}: Also known as \textit{Commit and Reveal}, is a cryptographic primitive that enables one to commit to a value (\eg statement, document, \etc}) while keeping it a secret and on a later time reveal the committed value~\cite{brassard1988minimum}. Commitment scheme is a good method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.
